Paper Analysis

### 2025-05-23 Paper_WriteUp/Paper_Plots.qmd
all experiential plots to have same x axis width

#plot
winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  xlim(c(-0.075, 0.075)) +
  theme_single_y()

@@

## then the winner effects plot
winner_plot_gm <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |>
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "GM Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  xlim(c(-0.075, 0.075)) +
  theme_single_y()

@@

#plot
winner_plot_20_22 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "2000-2200 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

```{r figure-s1-right}
#| eval: false
#read in model
fit_20_22_bullet_prev = readRDS(here("results_revision", "lichess2300-2500", "all_rated_bullet_model_n1.RDS"))

#read in users
bullet_20_22 = readRDS(here("results_revision", "lichess2300-2500", "users_bullet.RDS"))

@@

#plot
winner_plot_23_25 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "2300-2500 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

>>>>

#plot
winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  scale_x_continuous(breaks = c(-0.06, -0.03, 0, 0.03, 0.06), 
                     labels = c(-0.06, -0.03, 0, 0.03, 0.06),
                     limits = c(-0.062, 0.062)) +
  theme_single_y()

@@

## then the winner effects plot
winner_plot_gm <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |>
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "GM Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  scale_x_continuous(breaks = c(-0.06, -0.03, 0, 0.03, 0.06), 
                     labels = c(-0.06, -0.03, 0, 0.03, 0.06),
                     limits = c(-0.062, 0.062)) +
  theme_single_y()

@@

#plot
winner_plot_20_22 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "2000-2200 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  scale_x_continuous(breaks = c(-0.06, -0.03, 0, 0.03, 0.06), 
                     labels = c(-0.06, -0.03, 0, 0.03, 0.06),
                     limits = c(-0.062, 0.062)) +
  theme_single_y()

@@

```{r figure-s1-right}
#| eval: false
#read in model
fit_23_25_bullet_prev = readRDS(here("results_revision", "lichess2300-2500", "all_rated_bullet_model_n1.RDS"))

#read in users
bullet_23_25 = readRDS(here("results_revision", "lichess2300-2500", "users_bullet.RDS"))

@@

#plot
winner_plot_23_25 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "2300-2500 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  scale_x_continuous(breaks = c(-0.06, -0.03, 0, 0.03, 0.06), 
                     labels = c(-0.06, -0.03, 0, 0.03, 0.06),
                     limits = c(-0.062, 0.062)) +
  theme_single_y()
